---
title: "Genome size of sequenced genomes available on NCBI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This is a document to create plots of data on genome size from NCBI (as of 20.06.19). Here I plot genome size against the year it was released for all the genomes available on NCBI. I also plot the distribution of log genome size using a kernel denisty function. After loading data "NCBI_eukaryotes.txt" with read.table, run the following commands to recreate these plots.

```{r, include=FALSE}
setwd("/Users/stapley/Dropbox/Gsize")
dat = read.table("NCBI_eukaryotes.txt", header = TRUE)
```

## Sequenced genome size over time for different taxonomic groups

Genomes on NCBI have been getting bigger. The Axolotl genome is the largest. 

```{r}
library(scales)
dat$l.Gsize = log(dat$G.Size.Mb)
par(bty="l")
plot(G.Size.Mb~year, typ="n", dat, ylab="Genome Size (Mb)", xlab="Year", ylim=c(0,37000))
points(G.Size.Mb~year, pch=19, subset(dat, dat$group1=="Plants"), col=alpha("green3", 0.75))
points(G.Size.Mb~I(year+0.25), pch=19, subset(dat, dat$group1=="Animals"), col=alpha("blue3", 0.75))
points(G.Size.Mb~I(year+0.5), pch=19, subset(dat, dat$group1=="Fungi"), col=alpha("orange", 0.75))
points(G.Size.Mb~I(year+0.75), pch=19, subset(dat, dat$group1=="Protists"), col=alpha("red", 0.75))

```

## Distribution of sequenced genome sizes for different taxonomic groups

```{r}
plants <-  subset(dat, dat$group1=="Plants")
animals <-  subset(dat, dat$group1=="Animals")
fungi <- subset(dat, dat$group1=="Fungi")
protists <- subset(dat, dat$group1=="Protists")

par(bty="l")
plot(density(dat$l.Gsize), ylab="", col="white", main="Log genome size", ylim=c(0,1))
lines(density(plants$l.Gsize), col="dark green")
lines(density(animals$l.Gsize), col="blue")
lines(density(fungi$l.Gsize), col="orange")
lines(density(protists$l.Gsize),col="red")


```

